Effect of character correlation

### 2018-03-26 Analysis/04-EffectCorrelation_lm.Rmd
Added pooled analysis (dodgy)

```{r, message = FALSE}
## Loading and calculating all the matrices CDs
all_matrices_cd <- get.all.matrix.CD(path = "../Data/Simulations/Matrices", verbose = TRUE, length.out = 35, cent.tend = mean)
save(all_matrices_cd, file = "../Data/matrices_cd.Rda")
# load("../Data/matrices_cd.Rda")
```

@@

```{r}
## Pool all the results into one list
pooled_results <- pool.matrix.cd(all_matrices_cd)

## Running the model
model_out_bay_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", cent.tend = NULL)
model_out_bay_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "Triplets", cent.tend = NULL)
model_out_par_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "RF", cent.tend = NULL)
model_out_par_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", cent.tend = NULL)

>>>>

```{r, message = FALSE}
## Loading and calculating all the matrices CDs
# all_matrices_cd <- get.all.matrix.CD(path = "../Data/Simulations/Matrices", verbose = TRUE, length.out = 35, cent.tend = mean)
# save(all_matrices_cd, file = "../Data/matrices_cd.Rda")
load("../Data/matrices_cd.Rda")
```

@@

```{r, fig.width=12, fig.height=12, warnings = FALSE}
## Pool all the results into one list
pooled_results <- pool.matrix.cd(all_matrices_cd, length.out = 28)

# ## Running the model
model_out_bay_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "RF", cent.tend = NULL)
model_out_bay_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Bayesian", metric = "Triplets", cent.tend = NULL)
model_out_par_RF <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "RF", cent.tend = NULL)
model_out_par_Tr <- run.lm(pooled_results, whole_data, chain = "pool", method = "Parsimony", metric = "Triplets", cent.tend = NULL)
